% Appendix - Theoretical Derivations
% Marked separately so it can be transcribed by hand at the end of the project.

\appendix

\section{Theoretical Derivations}
\label{app:theory}

This appendix collects the analytical results that motivate the experimental design.
Where a result is classical, we cite the canonical source and give a compact
derivation suitable for transcription by hand. Where the result is a novel synthesis
of standard pieces, we mark it with a $\star$.

Throughout this appendix, $f \colon \mathbb{R}^d \to \mathbb{R}^d$ denotes an
autonomous vector field for the classical numerical-analysis statements, and
$J(x) = \partial f / \partial x$ is its Jacobian. For the Neural ODE experiments
we write $f_\theta(x,t)$ and $\fjac(x,t) = \partial f_\theta(x,t)/\partial x$.

\subsection{Linear stability and the step-size restriction (Mechanism B)}
\label{app:stability}

\begin{theorem}[Stability step bound, after Hairer--Wanner~\cite{hairer1996solving}]
\label{thm:stability}
Let $\Phi_h$ be an explicit Runge--Kutta method with stability region $S \subset
\mathbb{C}$, and apply it to the linear test equation $\dot y = \lambda y$.
The numerical scheme is stable iff $h\lambda \in S$. For a nonlinear system
$\dot x = f(x)$ in the neighborhood of a point $x^\star$ where $f(x^\star) = 0$,
local stability of $\Phi_h$ requires
\begin{equation}
h \cdot \rho(J(x^\star)) \;\leq\; C_p,
\label{eq:stability-bound}
\end{equation}
where $\rho(\cdot)$ denotes spectral radius and $C_p$ is a method-dependent constant
(for classical RK4, $C_p \approx 2.78$ on the negative real axis).
\end{theorem}

\begin{proof}[Sketch]
The standard linearisation argument: write $x = x^\star + y$, expand
$f(x^\star + y) = J(x^\star) y + O(\|y\|^2)$, and apply $\Phi_h$ to the linearised
system. Stability is then a property of the eigenvalues of the amplification matrix
$R(hJ)$, which equals $\Phi_h$ applied to $\dot y = \lambda y$ for each eigenvalue
$\lambda$ of $J(x^\star)$. The condition $h\lambda \in S$ is therefore necessary and
sufficient for local linear stability. See~\cite{hairer1996solving} \S IV.2 for the
full argument.
\end{proof}

\textbf{Consequence.} On a \emph{stiff} system, $\rho(J) \gg 1$, so the stable step
size $h_\text{stab} = C_p / \rho(J)$ can be much smaller than the step size required
for accuracy alone. This is the mechanism that explicit methods are penalised on
stiff problems.

\textbf{Trajectory-local version.} The equilibrium calculation is the cleanest
way to state the stability mechanism, but the experiments in this paper do not
measure Jacobians only at equilibria. Along a trajectory $x(t)$, the local
variational equation is
\begin{equation}
\dot{\delta x}(t) = J(x(t),t)\,\delta x(t).
\label{eq:trajectory-linearization}
\end{equation}
Thus the reported $\rho(J(x(t),t))$, $\|J(x(t),t)\|_F$, and accepted step sizes
should be read as trajectory-local diagnostics of the learned dynamics, not as
global stiffness certificates. They indicate whether the numerical solve is
encountering locally restrictive Jacobians on the validation trajectories in
this setup.

\subsection{Frobenius norm bounds the spectral radius}
\label{app:frobenius-bound}

\begin{lemma}[Frobenius dominance]
\label{lem:frob-dominates}
For any matrix $A \in \mathbb{R}^{d \times d}$,
\begin{equation}
\rho(A) \;\leq\; \|A\|_2 \;\leq\; \|A\|_F,
\label{eq:frob-bound}
\end{equation}
with equality in the first inequality iff $A$ is normal, and equality in the second
iff $A$ has at most one nonzero singular value.
\end{lemma}

\begin{proof}
Let $\sigma_1 \geq \dots \geq \sigma_d \geq 0$ be the singular values of $A$. Then
$\|A\|_2 = \sigma_1$ and $\|A\|_F^2 = \sum_i \sigma_i^2$, so
$\|A\|_2 \leq \|A\|_F$. For any eigenvalue $\lambda$ of $A$ with eigenvector $v$,
$\|Av\| = |\lambda| \|v\|$, hence $|\lambda| \leq \|A\|_2$. Taking the maximum over
eigenvalues yields $\rho(A) \leq \|A\|_2$.
\end{proof}

\textbf{Consequence.} The penalty $\lambda_J \|J\|_F^2$ is a soft, differentiable
upper bound on $\lambda_J \rho(J)^2$. Suppressing $\|J\|_F$ therefore makes a
smaller spectral radius plausible, but Lemma~\ref{lem:frob-dominates} does not
imply proportional shrinkage of $\rho(J)$. The stability benefit requires
spectral engagement: the eigenvalues that constrain the step size must actually
move, not merely the Frobenius upper bound.

\subsection{Truncation-error step bound (Mechanism A)}
\label{app:trunc-bound}

\begin{theorem}[Accuracy step bound, after Hairer--N\o{}rsett--Wanner~\cite{hairer1993solving}]
\label{thm:accuracy}
For an order-$p$ Runge--Kutta method in an idealised scalar-tolerance regime,
with adaptive step size satisfying an error tolerance $\tau$, the expected
number of steps to integrate over $[0, T]$ obeys
\begin{equation}
N \;\leq\; C \cdot T \cdot M^{p/(p+1)} \cdot \tau^{-1/(p+1)},
\label{eq:accuracy-bound}
\end{equation}
where $M = \sup_{t \in [0,T]} \|x^{(p+1)}(t)\|$ and $C$ depends only on the method.
\end{theorem}

\begin{proof}[Sketch]
The local truncation error of an order-$p$ method is
$\tau_n = \frac{h^{p+1}}{(p+1)!} x^{(p+1)}(\xi_n) + O(h^{p+2})$ for some
$\xi_n \in [t_n, t_{n+1}]$. The optimal adaptive step satisfies
$h^{p+1} M \approx \tau$, so $h \approx (\tau / M)^{1/(p+1)}$. The number of steps is
$N \approx T / h$. See~\cite{hairer1993solving} \S II.4.
\end{proof}

\textbf{Connection to Jacobians.} For an autonomous ODE, the first few time
derivatives illustrate why Jacobian regularization can affect the local-error
constant:
\begin{align}
x''(t)
  &= \frac{d}{dt} f(x(t))
   = J(x(t)) f(x(t)), \\
x'''(t)
  &= \frac{d}{dt}\bigl(J(x(t)) f(x(t))\bigr)
   = J(x(t))^2 f(x(t)) + \bigl(DJ(x(t))[f(x(t))]\bigr) f(x(t)).
\end{align}
The second term in $x'''$ contains Hessian information for $f$. Higher
derivatives similarly involve products of Jacobians and higher derivatives of
the vector field. Suppressing Jacobian norms can therefore reduce the
local-error scale $M$, but $\|J\|_F$ alone does not determine $M$.

\textbf{Practical tolerance caveat.} Practical embedded adaptive solvers do not
usually enforce a pure scalar tolerance. They control a weighted error norm
whose components are scaled roughly as
\begin{equation}
\left|
\frac{e}{a_\text{tol} + r_\text{tol}\,|x|}
\right|.
\label{eq:weighted-error-norm}
\end{equation}
Because our tolerance sweep co-scales $a_\text{tol}$ and $r_\text{tol}$ and
re-trains a separate model in each tolerance cell, the observed exponent in
\S\ref{sec:h0} should be interpreted as consistency with expected solver
behavior, not as a clean asymptotic estimate of $r_\text{tol}^{-1/(p+1)}$ for
one fixed learned vector field.

\subsection{Hutchinson estimator for the Frobenius norm squared}
\label{app:hutchinson}

\begin{theorem}[Hutchinson unbiasedness, after Hutchinson~\cite{hutchinson1990stochastic}]
\label{thm:hutchinson}
Let $A \in \mathbb{R}^{d \times d}$ and let $\epsilon \in \mathbb{R}^d$ be a random
vector with $\mathbb{E}[\epsilon] = 0$ and $\mathbb{E}[\epsilon \epsilon^\top] = I_d$
(e.g., $\epsilon$ has i.i.d.\ Rademacher entries, or i.i.d.\ $\mathcal{N}(0,1)$).
Then
\begin{equation}
\mathbb{E}_\epsilon\!\left[\|A^\top \epsilon\|^2\right] \;=\; \|A\|_F^2.
\label{eq:hutchinson}
\end{equation}
\end{theorem}

\begin{proof}
\begin{align}
\mathbb{E}_\epsilon\!\left[\|A^\top \epsilon\|^2\right]
&= \mathbb{E}\left[\epsilon^\top A A^\top \epsilon\right]
 = \mathbb{E}\!\left[\mathrm{tr}\!\left(A A^\top \epsilon \epsilon^\top\right)\right] \\
&= \mathrm{tr}\!\left(A A^\top \, \mathbb{E}[\epsilon \epsilon^\top]\right)
 = \mathrm{tr}(A A^\top)
 = \|A\|_F^2.
\end{align}
\end{proof}

\textbf{Variance bound.} For Rademacher $\epsilon$,
$\mathrm{Var}[\|A^\top \epsilon\|^2] = 2 \sum_{i \neq j} (AA^\top)_{ij}^2$, which is
zero iff $AA^\top$ is diagonal. A $K$-sample average reduces variance by $1/K$.

\textbf{Implementation.} In automatic differentiation, $A^\top \epsilon$ is the
vector--Jacobian product of $f$ at the evaluation point with co-tangent vector
$\epsilon$, which costs a single backward pass through $f$ regardless of $d$.

\subsection{Van der Pol Jacobian calibration}
\label{app:vdp-jac-calibration}

The Van der Pol target used in the engagement analysis is
\begin{equation}
\dot{x}_1 = x_2,
\qquad
\dot{x}_2 = \mu(1-x_1^2)x_2 - x_1.
\end{equation}
Writing $f_\mathrm{vdp}(x) = (f_1(x), f_2(x))^\top$, the partial derivatives are
\begin{align}
\frac{\partial f_1}{\partial x_1} &= 0,
&
\frac{\partial f_1}{\partial x_2} &= 1, \\
\frac{\partial f_2}{\partial x_1} &= -2\mu x_1 x_2 - 1,
&
\frac{\partial f_2}{\partial x_2} &= \mu(1-x_1^2).
\end{align}
Thus
\begin{equation}
J_{\mathrm{vdp}}(x)
=
\begin{pmatrix}
0 & 1 \\
-2\mu x_1x_2 - 1 & \mu(1-x_1^2)
\end{pmatrix}.
\label{eq:vdp-jacobian}
\end{equation}
The squared Frobenius norm is the sum of squared entries:
\begin{equation}
\|J_{\mathrm{vdp}}(x)\|_F^2
=
1 + (-2\mu x_1x_2 - 1)^2 + \mu^2(1-x_1^2)^2.
\label{eq:vdp-frob-squared}
\end{equation}
Table~\ref{tab:true-jac-calibration} in the main text evaluates
\eqref{eq:vdp-frob-squared} analytically on the same validation-time subsample
used for learned-Jacobian diagnostics. This makes the calibration a
true-target comparison on the diagnostic support rather than a separate global
property of the Van der Pol vector field.

\subsection{Ground-truth versus learned-trajectory penalty support}
\label{app:penalty-mismatch}

The implemented penalty samples states from the ground-truth trajectory
distribution. Abstracting away the Hutchinson estimator, it is
\begin{equation}
R_{\mathrm{gt}}(\theta)
=
\mathbb{E}_{(x,t)\sim \mu_{\mathrm{gt}}}
\left[\|\fjac(x,t)\|_F^2\right].
\label{eq:r-gt}
\end{equation}
An augmented-state implementation instead integrates the penalty along the
model's own trajectory:
\begin{equation}
R_{\mathrm{model}}(\theta)
=
\mathbb{E}_{x_0}
\int_0^T
\left\|\fjac\!\left(\hat{x}_\theta(t;x_0),t\right)\right\|_F^2\,dt.
\label{eq:r-model}
\end{equation}
The two regularizers are close only when
\begin{equation}
\hat{x}_\theta(t;x_0) \approx x_{\mathrm{gt}}(t;x_0)
\label{eq:trajectory-fit-condition}
\end{equation}
on the time interval and initial-condition distribution of interest, and when
the Jacobian norm does not vary too sharply between the two state supports.
In the poor-fit $\mu=50$ regime, the regularizer can therefore be weak for two
distinct reasons: the learned vector field may have already collapsed to a
low-Jacobian field, and the ground-truth penalty may be evaluated on states
that the learned trajectory does not actually visit. The present experiment
does not separate these mechanisms; it conflates low-Lipschitz collapse with
penalty-support mismatch.

\subsection{Penalty-engagement diagnostics}
\label{app:engagement-criterion}

Write the regularized objective as
\begin{equation}
L(\theta)=L_{\mathrm{task}}(\theta)+\lambda_J R(\theta).
\label{eq:regularized-objective}
\end{equation}
A direct engagement diagnostic is the gradient-ratio
\begin{equation}
\eta_J(\theta)
=
\frac{\lambda_J \left\|\nabla_\theta R(\theta)\right\|}
{\left\|\nabla_\theta L_{\mathrm{task}}(\theta)\right\|}.
\label{eq:gradient-ratio}
\end{equation}
The regularizer can only shape training when $\eta_J(\theta)$ is non-negligible.
Its direction also matters. A useful companion diagnostic is the gradient
alignment
\begin{equation}
\cos(\nabla L_{\mathrm{task}},\nabla R)
=
\frac{
\left\langle \nabla_\theta L_{\mathrm{task}}(\theta),
\nabla_\theta R(\theta)\right\rangle
}{
\left\|\nabla_\theta L_{\mathrm{task}}(\theta)\right\|
\left\|\nabla_\theta R(\theta)\right\|
}.
\label{eq:gradient-cosine}
\end{equation}
If this cosine is near zero, the regularizer may be mostly orthogonal to the
task update; if it is strongly positive in the convention of gradient descent
on $L_{\mathrm{task}}+\lambda_J R$, the two objectives pull in similar
descent directions; if it is strongly negative, reducing the task loss and
reducing the penalty are locally in conflict.

The back-of-envelope calculation in \S\ref{sec:engagement} compares loss
scales, not gradient norms. It is a useful sanity check for why the
$\mu=50$ penalty may be hard to see, but it is not direct evidence about
\eqref{eq:gradient-ratio} or \eqref{eq:gradient-cosine}, especially under Adam's
per-parameter rescaling. Logging $\eta_J$ and the cosine during training would
be the appropriate diagnostic for the proposed mechanism.

\subsection{A-stability of implicit Euler}
\label{app:a-stability}

\begin{theorem}[A-stability of implicit Euler, after Dahlquist~\cite{dahlquist1963special}]
\label{thm:a-stability}
The implicit Euler method $x_{n+1} = x_n + h f(x_{n+1})$ applied to the linear test
equation $\dot y = \lambda y$ with $\mathrm{Re}(\lambda) < 0$ is stable for every
$h > 0$.
\end{theorem}

\begin{proof}
On $\dot y = \lambda y$, the scheme reduces to $y_{n+1} = y_n + h \lambda y_{n+1}$,
so $y_{n+1} = (1 - h\lambda)^{-1} y_n$. For $\mathrm{Re}(\lambda) < 0$,
$|1 - h\lambda|^2 = (1 - h\mathrm{Re}(\lambda))^2 + (h\mathrm{Im}(\lambda))^2 > 1$
for all $h > 0$, hence $|1 - h\lambda|^{-1} < 1$ and $|y_{n+1}| < |y_n|$. The scheme
is therefore stable for all $h > 0$. Moreover $|1 - h\lambda|^{-1} \to 0$ as
$h \to \infty$, so the method is also L-stable.
\end{proof}

\textbf{Consequence.} On a stiff system, the implicit Euler step size is governed
only by accuracy (Mechanism A), not by stability (Mechanism B). Each step, however,
requires solving a nonlinear equation; for a Newton-based implicit solver this is
$O(\bar K)$ Jacobian evaluations and linear solves per step.

\subsection{The interaction prediction \texorpdfstring{$\star$}{star}}
\label{app:interaction}

We now combine the preceding results to derive the prediction that motivated the
original H1 hypothesis. Let $s$ index target-system stiffness and define the
fractional NFE reduction at matched validation MSE as
$\delta(s) := 1 - N_\text{reg}(s)/N_\text{base}(s)$. The original proposal used a
single shrinkage factor $\beta$ as a shorthand. That is too strong: Frobenius
shrinkage, spectral-radius shrinkage, and local-error shrinkage need not
coincide. We therefore distinguish
\begin{equation}
\beta_F =
\frac{\|J_{\mathrm{reg}}\|_F}{\|J_{\mathrm{base}}\|_F},
\qquad
\beta_\rho =
\frac{\rho(J_{\mathrm{reg}})}{\rho(J_{\mathrm{base}})},
\qquad
\beta_M =
\frac{M_{\mathrm{reg}}}{M_{\mathrm{base}}},
\label{eq:beta-definitions}
\end{equation}
where $M$ is the local-error derivative scale from
Theorem~\ref{thm:accuracy}. In the experiments these quantities should be read
as trajectory-local summaries on the validation diagnostic grid, not as global
properties of the vector field.

By Theorem~\ref{thm:accuracy}, on the smooth task
\begin{equation*}
\frac{N_\text{reg}}{N_\text{base}}
  = \left(\frac{M_\text{reg}}{M_\text{base}}\right)^{p/(p+1)}
  = \beta_M^{p/(p+1)},
\end{equation*}
so the fractional NFE reduction is approximately
$1 - \beta_M^{p/(p+1)}$ when the solve is accuracy-limited.

By Theorem~\ref{thm:stability}, on the stiff task
$N \propto T \cdot \rho(J) / C_p$, so
\begin{equation*}
\frac{N_\text{reg}}{N_\text{base}} \approx \beta_\rho,
\end{equation*}
and the fractional NFE reduction is approximately $1-\beta_\rho$ when the
solve is stability-limited. Lemma~\ref{lem:frob-dominates} only gives
$\rho(J) \leq \|J\|_F$: reducing $\|J\|_F$ makes a reduction in $\rho(J)$
plausible, but it does not guarantee $\beta_\rho \approx \beta_F$.

\begin{proposition}[Conditional interaction prediction]
\label{prop:interaction}
Suppose the smooth task is accuracy-limited, the stiff task is
stability-limited, and regularization engages both the accuracy scale
($\beta_M<1$) and the stability scale ($\beta_\rho<1$) at matched validation
MSE. Then the predicted ratio of fractional NFE reductions is
\begin{equation}
\frac{\delta_\text{stiff}}{\delta_\text{smooth}}
  \;\approx\; \frac{1 - \beta_\rho}{1 - \beta_M^{p/(p+1)}}.
\label{eq:interaction-prediction}
\end{equation}
A positive interaction requires this ratio to exceed one; equivalently, the
spectral-radius engagement in the stability-limited regime must be strong
enough relative to the accuracy-scale engagement in the accuracy-limited
regime. It is not implied by $\beta_F<1$ alone.
\end{proposition}

\textbf{Empirical caveat.} The antecedent of
Proposition~\ref{prop:interaction} is exactly what fails in this experiment.
At $\mu=50$, the Frobenius penalty is operationally inert because the learned
field is already low-Jacobian; at $\mu=10$, where Frobenius engagement is
visible, the learned dynamics do not show a stability-limited step-size
restriction. The proposition therefore does not prove the empirical trade-off.
It states a conditional mechanism for a hypothetical regime in which fit,
penalty engagement, and learned stiffness co-occur.

\subsection{Cost decomposition for implicit Runge--Kutta}
\label{app:implicit-cost}

\begin{proposition}[Implicit cost decomposition]
\label{prop:implicit-cost}
For an $s$-stage implicit Runge--Kutta method run for $N$ outer steps, with average
Newton iteration count $\bar K$ per step, the cumulative work is
\begin{equation}
W \;=\; N \cdot \bar K \cdot \bigl[s \cdot W_f \;+\; W_J \;+\; W_\text{lin}\bigr],
\label{eq:implicit-cost}
\end{equation}
where $W_f$ is the cost of one $f$ evaluation, $W_J$ the cost of one Jacobian
evaluation, and $W_\text{lin}$ the cost of a single linear solve of dimension
$d \cdot s$.
\end{proposition}

Equation~\eqref{eq:implicit-cost} is the cost model for serious Newton-based
stiff solvers such as implicit Runge--Kutta, BDF, or Radau-type methods. In
that setting, the NFE count alone (which is $N \cdot \bar K \cdot s$ for
implicit Runge--Kutta) is not sufficient to characterize wall-clock cost; the
Jacobian and linear-solve terms can dominate on small $d$ where dense linear
algebra is cheap but $W_J$ is non-trivial.

This is not the exact cost model for the empirical H3 baseline:
\texttt{torchdiffeq.implicit\_adams} uses fixed-point iteration rather than
Newton solves. Its leading per-step cost is closer to
$N \cdot \bar K_\mathrm{fp} \cdot W_f$, with no explicit Jacobian or linear-solve
term exposed to the user. It also does not represent a full comparison against
modern $A$- or $L$-stable Newton-based stiff solvers. Proposition~\ref{prop:implicit-cost}
therefore motivates why implicit methods can have hidden costs, but it does
not describe the exact implementation used in the H3 comparison.

\section{Reproducibility Checklist}
\label{app:reproducibility}

This checklist records settings not already stated in \S\ref{sec:methods}; we
do not duplicate model, optimizer, training, or solver descriptions that
appear in the main text.

\begin{enumerate}[leftmargin=2em]
\item \textbf{Software.} Python 3.10.5, PyTorch 2.11.0, torchdiffeq
0.2.5~\citep{chen2018torchdiffeq}, NumPy 2.2.6, SciPy 1.15.3,
matplotlib 3.10.9. Hardware: Apple Silicon laptop, CPU-only training.
Total wall time for the 150-run sweep inventory: $\approx 9$ hours.
\item \textbf{Wall-clock measurement protocol.} Each cell's reported
wall-clock per forward pass is a single timed call to
\texttt{model(x0\_val, t)} under \texttt{torch.no\_grad()}, with no warm-up
pass. On CPU this is noisy at the millisecond level; we recommend
reproducing with at least three timed passes per cell if precise wall-clock
numbers matter to the downstream conclusion.
\item \textbf{IC generator ordering.} For each seed, a single
\texttt{torch.Generator(seed)} is used to draw the $256$ training $x_0$
samples and then the $64$ validation samples (disjoint, consecutive draws
from the same generator). The global PyTorch RNG is independently seeded
with the same integer for model initialisation and Hutchinson noise.
\item \textbf{Penalty sampling distribution.} 32 $(t, x)$ pairs per training
step are drawn uniformly from the \emph{flat} $(T \cdot B)$ index of
ground-truth training trajectories, so time and initial-condition indices
are sampled jointly with equal weight. This implicitly over-samples
slow-manifold portions of the Van der Pol trajectory where the
uniform-in-$t$ grid is dense.
\item \textbf{Tolerance sweep coupling.} $r_\text{tol}$ and $a_\text{tol}$
are both varied in the tolerance sweep:
$(r_\text{tol}, a_\text{tol}) \in \{(10^{-3}, 10^{-5}), (10^{-5}, 10^{-7}),
(10^{-7}, 10^{-9})\}$. The fitted exponent $\alpha$ in \S\ref{sec:h0}
therefore reflects sensitivity to both tolerances jointly. The tolerance
override is applied before training, so these cells are train-and-evaluate
tolerance settings rather than an eval-only sweep on one fixed trained model.
\item \textbf{Solver-registry mutation.} Tolerance overrides are implemented
by in-process mutation of \texttt{SOLVER\_REGISTRY} in
\texttt{scripts/train\_single.py}. Each cell runs in a fresh subprocess
(via \texttt{run\_matrix.py}) so the mutation does not leak across cells.
\item \textbf{Statistical tests.} Paired Wilcoxon signed-rank with the
\emph{wilcox} zero-handling convention; rank-biserial correlation as effect
size. Bonferroni correction is applied at family-wise $\alpha = 0.05$
across the H3 set ($m = 3$). With each H3 comparison hitting one-sided
$p = 0.031$ uncorrected, none survives Bonferroni at $\alpha/m = 0.017$
when treated as a family. We therefore report the consistent direction
across $\mu$ as the substantive finding, not the per-comparison
significance after correction.
\item \textbf{Result provenance.} Result filenames encode task, solver,
$\lambda_J$, and seed; full metadata such as $\mu$, $K$, tolerance overrides,
and the output directory for follow-up sweeps must be read from the JSON
\texttt{config} block and directory structure. A cleaner archival release
would include a manifest or filenames containing every experimental factor.
\item \textbf{Total runs.} 150 trained runs across all sweeps,
summarised in Table~\ref{tab:cells} of the main text.
\end{enumerate}
